---
title: "Visualization"
subtitle: "Part I"
output: github_document
---

```{r}
library(tidyverse)
library(ggridges)
```

## Load the weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(                       # pull data from online
    c("USW00094728", "USC00519397", "USS0023B17S"), # weather stations
    var = c("PRCP", "TMIN", "TMAX"),                # variables
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```


## Scatterplots

Create my first scatterplot ever.

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + # default range have to set geometry
  geom_point()  
```

New approach, same plot.

```{r}
weather_df %>% 
  #data manipulaiton
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Save and edit a plot object.

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) 

weather_plot + geom_point()
```

## Advanced scatterplot

Start with the same one and make it fancy

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE)
```

What about the 'aes' placement

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) + # color only applies to the scatterplot
  geom_smooth() # color does not apply to the lines 
```

Lets facet some things

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + #alpha = tmin
  geom_point() + # alpha = .5 -> 50% transparency  
  geom_smooth(se = FALSE, size = 1) +
  facet_grid(. ~ name) #.means nothing define row
  # facet_grid(name ~ .) reversed order
```

Let's combine some elements and try a new plot

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```


##  Some small notes

How many geoms have to exist? 

You can have whatever geoms you want.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

You can use a neat geom

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  #geom_hex() # geom_bin2d()
  geom_density2d() +
  geom_point(alpha = .3)
```

## Univariate plots

Histograms are really great.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

Can we add color

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() +      # (position = "dodge")
  facet_grid(. ~ name)
```

Let's try a new geometry

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3, adjust = .5) # histogram with edges smoothed adjust can give more information
```

What about box plot?

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot()
```

Trendy plots :-)

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = .5) +
  stat_summary(fun = "median") #default maybe mean
```

Ridge plots -- most popular plot of 2017

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```

## Save and Embed 
```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)
  
ggsave("./results/weather_plot.pdf", weather_plot, width = 8, height = 5)
```

What about embedding...

```{r}
weather_plot
```

